% Copyright: CSCE240-001 - Fall 2016 - Group 7. All rights reserved.
% Date: 2016-12-01
%
% This chapter describes the OneVoter class.
% This class is an instance of a single voter to be used in the simulation program.

\chapter{OneVoter}

\vspace{-1.0cm}

The OneVoter class is used to represent a single voter to be used in the voting simulation.

\section{Constructor}
The Constructor for the OneVoter class takes in three integers as parameters.  These integers assign values to the Voter's sequence\_,time\_arrival\_seconds\_, and time\_vote\_duration\_seconds\_ variables.  The Time\_Start\_voting\_seconds\_ and which\_station variables are set to default values 0 and -1 by the constructor.

\section{General Functions}

\subsection{AssignStation}

This function takes in station\_number and start\_time\_seconds, and uses the data to calculate which station the voter will use, total time spent voting, and total time spent waiting to vote.

\subsection{GetTimeDoneVoting}
This Calculates time spent voting by adding time\_start\_voting\_seconds\_ and time\_vote\_duration\_seconds\_.

\subsection{GetTimeInQ}
Returns the time spent in the voting queue for a single voter by subtracting time\_arrival\_seconds\_ from time\_start\_voting\_seconds\_.

\subsection{GetTOD}
Returns the time of day at which the voter voted.

\subsection{ConvertTime}
Returns the time with hours, minutes and seconds. Accepts the time in seconds from start of day that the voter voted. This function is called by \texttt{GetTOD}.
